% =============================================================
%  Payne (Pei En) Yeh — Curriculum Vitae
%  Edit this file, push to GitHub → public/cv.pdf auto-updates
% =============================================================
\documentclass[10pt, a4paper]{article}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[top=1.5cm, bottom=1.5cm, left=2cm, right=2cm]{geometry}
\usepackage[hidelinks, colorlinks=true, urlcolor=black]{hyperref}
\usepackage{fontawesome5}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{parskip}

\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}

% ---- Section style (bold heading + full-width rule) ----------
\titleformat{\section}
  {\bfseries\large}{}{0em}{}
  [\vspace{-4pt}\rule{\linewidth}{0.6pt}\vspace{2pt}]
\titlespacing*{\section}{0pt}{10pt}{4pt}

% ---- List style ----------------------------------------------
\setlist[itemize]{noitemsep, topsep=2pt, parsep=0pt, leftmargin=1.4em}

% ---- Work / project entry ------------------------------------
% \workentry{Role}{Company}{Tech | Period}{bullets}
\newcommand{\workentry}[4]{%
  \noindent\textbf{#1}\\[-1pt]
  \textit{#2}\\[-3pt]
  {\small\textcolor[gray]{0.4}{#3}}
  \begin{itemize}
    #4
  \end{itemize}
  \vspace{2pt}
}

% ---- Education entry -----------------------------------------
% \eduentry{School}{Period}{Degree + notes}
\newcommand{\eduentry}[3]{%
  \noindent\textbf{#1} \hfill \textit{\small #2}\\[-1pt]
  {\small #3}
  \vspace{4pt}
}

% ==============================================================
\begin{document}

% ---- HEADER --------------------------------------------------
\begin{center}
  {\LARGE\bfseries Payne (Pei En) Yeh}\\[5pt]
  {\small
    \faLinkedin\ \href{https://www.linkedin.com/in/payne-yeh-21362825b/}{linkedin.com/in/payne-yeh-21362825b}
    \enspace\textbar\enspace
    \faEnvelope\ \href{mailto:90727sam@gmail.com}{90727sam@gmail.com}
    \enspace\textbar\enspace
    \faPhone\ 0963-581-713
    \enspace\textbar\enspace
    \faGithub\ \href{https://github.com/Payne721401}{Payne721401}
  }
\end{center}

% ---- EDUCATION -----------------------------------------------
\section{Education}

\eduentry{National Taiwan University (NTU)}{Sep 2026 -- Jun 2028 (Expected)}
  {MS in Atmospheric Sciences \textit{(On Leave)}}

\eduentry{National Central University (NCU)}{Sep 2020 -- Jun 2024}
  {BS in Atmospheric Sciences \enspace\textbar\enspace AI Application Credit Program \enspace\textbar\enspace
   2024 NCU Outstanding Student Scholarship}

% ---- SKILLS --------------------------------------------------
\section{Skills}

\begin{itemize}
  \item \textbf{Languages}: Python, C/C++, SQL, JavaScript, Dart (Flutter)
  \item \textbf{Backend}: Django, Flask, Selenium, PostgreSQL, RESTful APIs
  \item \textbf{DevOps \& Infra}: Git, GitHub Actions (CI/CD), Docker, Linux, Cloudflare R2, Firebase
  \item \textbf{AI/ML}: PyTorch, TensorFlow, Scikit-learn
\end{itemize}

% ---- AWARDS & COMPETITIONS -----------------------------------
\section{Awards \& Competitions}

\begin{itemize}
  \item \textbf{1st Place,} NCU Sustainable Innovation Proposal Competition (2023)
  \item \textbf{2nd Place,} Weather Hackathon (2023) \textit{(Previously 3rd Place in 2022)}
  \item \textbf{Finalist (Notable Award),} National Smart Innovation Cross-disciplinary Competition (2023)
  \item \textbf{3rd Place,} NCU Campus Planning Proposal Competition (2020)
  \item NCU Outstanding Student Scholarship (2024)
\end{itemize}

% ---- WORK EXPERIENCE -----------------------------------------
\section{Work Experience}

\workentry
  {Freelance Backend Developer}
  {}
  {Python (Flask), RESTful APIs, PostgreSQL, TDD \enspace\textbar\enspace Apr 2025 -- Oct 2025}
  {\item Developed Python Flask RESTful APIs following Test-Driven Development (TDD) principles.
   \item Designed PostgreSQL database schemas and created indexes to optimize high-frequency queries.
   \item Achieved 100\% automated test coverage.}

\workentry
  {Ernst \& Young (EY) Consulting — Web Development \& Cybersecurity Intern}
  {}
  {Python (Django, Selenium), SQL \enspace\textbar\enspace Mar 2024 -- Jul 2024}
  {\item Architected an automated bidding crawler and search system based on Django MVC architecture.
   \item Optimized Python Selenium scraping scripts to process and structure thousands of external records.
   \item Analyzed banking AI and cybersecurity trends to assist in system compliance assessments.}

% ---- SELECTED PROJECTS ---------------------------------------
\section{Selected Projects}

\noindent\textbf{Taiwan AI Weather App} \enspace\textbar\enspace
  \href{https://github.com/Payne721401/taiwan-ai-weather}{[Github]} \enspace\textbar\enspace
  Flutter, Python, GitHub Actions, Firebase, Cloudflare R2\\
{\small Demo: \href{https://reurl.cc/O6ERE3}{https://reurl.cc/O6ERE3}}
\begin{itemize}
  \item Built a scalable decoupled architecture using Flutter, Python, Firebase, and Cloudflare R2.
  \item Automated CI/CD pipelines via GitHub Actions and implemented R2 caching to minimize server load.
  \item Integrated Firebase App Check and FreeRASP for multi-layer security against unauthorized API access.
\end{itemize}
\vspace{3pt}

\noindent\textbf{MQTT-based IoT Smart Classroom} \enspace\textbar\enspace
  C/C++, MQTT, ESP32, YOLOv8\\
{\small Demo: \href{https://reurl.cc/2a8lk9}{https://reurl.cc/2a8lk9}}
\begin{itemize}
  \item Developed ESP32 MCU (C/C++) and a Raspberry Pi MQTT broker for real-time sensor control.
  \item Integrated YOLOv8 for real-time occupancy counting to automate HVAC and lighting control.
  \item Awarded Finalist in the National Smart Innovation Cross-disciplinary Competition.
\end{itemize}
\vspace{3pt}

\noindent\textbf{HRV-based Sleep Stage Classification} \enspace\textbar\enspace
  Python, Scikit-learn, Signal Processing
\begin{itemize}
  \item Applied EMD on HRV signals to extract time-frequency features (SDNN, RMSSD, HF power).
  \item Trained Random Forest and Decision Tree models for 5-class sleep staging (Wake, N1, N2, N3, REM).
\end{itemize}
\vspace{3pt}

\noindent\textbf{Air Pollution Analysis — Kaohsiung Liveability} \enspace\textbar\enspace
  Python, Pandas, Atmospheric Science
\begin{itemize}
  \item Conducted EDA and descriptive statistics on PM2.5/AQI datasets across Kaohsiung districts.
  \item Produced insights for pollution control policy based on spatial trend analysis.
\end{itemize}

% ---- ACTIVITIES ----------------------------------------------
\section{Activities}

\noindent\textbf{NCU Athletics Team} — Long-Distance Athlete (5000m / 10000m) \hfill
  \textit{\small Sep 2020 -- Jun 2024}\\
{\small Represented NCU at National University Games (\,全大運\,) in 5000m and 10000m events.}

\vspace{5pt}
\noindent\textbf{NCU Cycling Club} — Officer, Teaching \& Visual Design \hfill
  \textit{\small Sep 2021 -- Jun 2023}\\
{\small Organized beginner cycling workshops and managed club Facebook/Instagram accounts.}

\vspace{5pt}
\noindent\textbf{紙船計畫 (Paper Boat Project)} — Volunteer Tutor \hfill
  \textit{\small 2022}\\
{\small Provided 110 hours of free online tutoring for students in Taitung (台東高中 / 台東新生國中).}

% ---- LANGUAGES -----------------------------------------------
\section{Languages}

\begin{itemize}
  \item \textbf{Chinese (Traditional)}: Native
  \item \textbf{English}: Professional Working Proficiency \enspace\textbar\enspace TOEIC 870
\end{itemize}

% ---- SPORTS ACHIEVEMENTS -------------------------------------
\section{Sports Achievements}

\begin{itemize}
  \item \textbf{Cycling}:\ \ 武嶺 KOM 3:13:52 — 1st Place, 96 Challenge Group;\enspace
        一日北高 $\approx$360\,km (Taipei to Kaohsiung)
  \item \textbf{Triathlon}: Standard 51.5\,km — 2:34:38, 7th Place M20 (2025 普悠瑪鐵人三項);\enspace
        泳渡日月潭 finisher
  \item \textbf{Running}:\ \ Half Marathon PB 1:24:27 (Taipei Marathon)
  \item \textbf{Hiking}:\ \ \ 14 of Taiwan's 百岳 (100 Major Peaks)
\end{itemize}

\end{document}
